Changes in accessibility to foodbanks during COVID-19 and implications for the food security of vulnerable populations in Hamilton, Ontario

### 2021-04-23 Accessibility-Foodbanks-Hamilton/Accessibility-Foodbanks-Hamilton.Rmd

```{r table-food-bank-info, echo=FALSE, results='asis'}
foodbank_table %>% kable("latex",
        booktabs = TRUE,
        align = ("cccccc"),
        col.names = c("Type", 
                      "Description", 
                      "Locations Pre-COVID", 
                      "Locations During COVID", 
                      "Additional Notes"),
        caption = "\\label{tab:food-bank-info}Food Bank and Food Service Information.",
        escape = FALSE) %>%
  kable_styling(latex_options = c("striped", "scale_down")) 
```

@@

```{r remove-irrelevant-destinations, include=FALSE}
## Remove entries in travel time matrices for inapplicable destinations
# As a first step, we will remove the computed travel times to the three Community Kitchen locations (IDs 1-3):
ttm_car <- ttm_car %>%
  filter(!between(OBJECTID, left = 1, right = 3))

```{r join-low-income-households, include=FALSE}
## Join proportion of low income households per DA to dwellings and total number of residential units:
dwelling_network_points_2016 <- dwelling_network_points_2016 %>%
  left_join(data_da_2016 %>%
              st_drop_geometry() %>%
              dplyr::transmute(DAUID = GeoUID, 
                               p_inc_less40k),
            by = "DAUID")
```

```{r probability-of-low-income-per-parcel, include=FALSE}
## Calculate probability that a point on the network will have low income households. This is the proportion of low income households in the DA multiplied by the total number of residential units at the point:
dwelling_network_points_2016 <- dwelling_network_points_2016 %>%
  mutate(income_less40k = p_inc_less40k * Dwellings)
```

```{r join-foodbank-data-to-travel-time-tables, include=FALSE}
## Data preparation
# Join the food bank data to the travel time tables:
ttm_car <- ttm_car %>%
  left_join(foodbank_locations %>%
              st_drop_geometry() %>%
              dplyr::select(ID, 
                            TYPE,
                            COVIDClose),
            by = c("OBJECTID" = "ID"))

@@

@@

```{r plot-levels-of-service, echo=FALSE, fig.cap="\\label{fig:levels-of-service}Levels of service at each facility pre-COVID-19 (top panel) and during COVID-19 (middle panel). The bottom panel shows the change in level of service."}
## Analysis
# Plot levels of service before and during covid

# Pre-covid
los_pre <- ggplot() +
  geom_sf(data = hamilton_cma) +
  geom_sf(data = los %>%
            filter(timing == "Pre-covid"),
          aes(color = los,
              size = los)) +
  geom_sf(data = foodbank_locations,
          aes(shape = COVIDClose)) +
  scale_color_distiller(palette = "OrRd", 
                        direction = 1) +
  scale_shape_manual(values = c("Yes" = 4, "No" = 1)) +
  theme_minimal()

# During covid
los_covid <- ggplot() +
  geom_sf(data = hamilton_cma) +
  geom_sf(data = los %>%
            filter(timing == "During covid"),
          aes(color = los,
              size = los)) +
  geom_sf(data = foodbank_locations,
          aes(shape = COVIDClose)) +
  scale_color_distiller(palette = "OrRd", 
                        direction = 1) +
  scale_shape_manual(values = c("Yes" = 4, "No" = 1)) +
  theme_minimal()

# This figure shows the places where the level of service deteriorated most (excluding the places that closed, where it vanished).
los_change <- los %>%
  st_drop_geometry() %>%
  pivot_wider(names_from = timing, 
              values_from = los, 
              values_fill = 0) %>%
  filter(`During covid` > 0) %>%
  mutate(los_d = `During covid` / `Pre-covid` - 1) %>%
  left_join(foodbank_locations %>%
            transmute(OBJECTID = ID,
                      geometry),
          by = "OBJECTID") %>%
  st_as_sf() %>%
  ggplot() +
  geom_sf(data = hamilton_cma) +
  geom_sf(aes(color = los_d,
              size = los_d)) +
  geom_sf(data = foodbank_locations,
          aes(shape = COVIDClose)) +
  scale_color_distiller(palette = "OrRd", 
                        direction = -1) +
  scale_shape_manual(values = c("Yes" = 4, "No" = 1)) +
  theme_minimal()

los_pre / los_covid / los_change
```

```{r plot-accessibility, echo=FALSE, fig.align = 'center', out.width = "90%", fig.cap="\\label{fig:accessibility}Accessibility by traffic analysis zone pre-COVID-19 (top panel) and during COVID-19 (middle panel). The bottom panel shows the change in accessibility."}
## Analysis
# Plot accessibility before and during covid:
acc_pre <- ggplot() +
  geom_sf(data = hamilton_cma) +
  geom_sf(data = accessibility_taz %>%
            filter(timing == "Pre-covid"),
          aes(fill = accessibility)) +
  scale_fill_distiller(palette = "OrRd", 
                        direction = 1) +
  theme_minimal()

acc_covid <- ggplot() +
  geom_sf(data = hamilton_cma) +
  geom_sf(data = accessibility_taz %>%
            filter(timing == "During covid"),
          aes(fill = accessibility)) +
  scale_fill_distiller(palette = "OrRd", 
                        direction = 1) +
  theme_minimal()

# Calculate accessibility change by TAZ:
accessibilty_taz_change <- accessibility_taz %>%
  st_drop_geometry() %>%
  pivot_wider(names_from = timing, 
              values_from = accessibility) %>%
  # Calculate changes in accessibility
  mutate(acc_d = `During covid` - `Pre-covid`) %>%
  # Join TAZ geometry
  left_join(population_age_income %>%
            transmute(TAZUID,
                      geometry),
          by = "TAZUID") %>%
  # Convert to simple features
  st_as_sf()

# Plot
acc_change <- ggplot() +
  geom_sf(data = hamilton_cma) +
  geom_sf(data = accessibilty_taz_change,
          aes(fill = acc_d),
          color = NA) +
  geom_sf(data = population_age_income,
          fill = NA) +
  scale_fill_fermenter(palette = "OrRd", 
                       direction = -1) +
  theme_minimal()

acc_pre / acc_covid / acc_change
```

>>>>

```{r table-food-bank-info, echo=FALSE, results='asis'}
foodbank_table %>% kable("latex",
        booktabs = TRUE,
        align = ("cccccc"),
        col.names = c("Type", 
                      "Description", 
                      "Locations Pre-COVID", 
                      "Locations During COVID", 
                      "Additional Notes"),
        caption = "\\label{tab:food-bank-info}Food Bank and Food Service Information.",
        escape = FALSE) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  column_spec(2, width = "15em") %>%
  column_spec(5, width = "15em")
```

@@

Figure \ref{fig:foodbanks} shows the location of the foodbanks in the City of Hamilton and their status. Before the pandemic there were `r nrow(foodbank_locations)` of which `r nrow(foodbank_locations %>% filter(COVIDClose == "Yes"))` closed during the pandemic. As seen in the figure, foodbanks tend to be predominantly located in the central parts of the city. This is not surprising: population density is high there, and it is also the part of the city where lower income households are more numerous in absolute and relative terms (see Figure \ref{fig:low-income-households}). Alas, this is also where most of the closures during the pandemic happened.

```{r plot-location-foodbanks, echo=FALSE, fig.cap="\\label{fig:foodbanks}Location of foodbanks and operation status; the dotted box is an inset of the central part of the City of Hamilton"}
## Analysis
# Plot location of foodbanks

# Create a bounding box for an inset
inset_box <- st_bbox(c(xmin = -79.975,
          xmax = -79.775, 
          ymax = 43.2, 
          ymin = 43.3), 
        crs = st_crs(4326)) %>%
  st_as_sfc()

fb <- ggplot() +
  geom_sf(data = hamilton_cma,
          fill = "lightgray") +
  geom_sf(data = foodbank_locations,
          aes(size = COVIDClose,
              shape = COVIDClose)) +
  geom_sf(data = inset_box,
          linetype = "dotted",
          color = "red",
          fill = NA) +
  scale_shape_manual(name = "Closed during COVID-19",
                     values = c("Yes" = 4, "No" = 1)) +
  scale_size_manual(values = c("Yes" = 3, "No" = 2)) +
  guides(size = FALSE) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "none")

fb_inset <- ggplot() +
  geom_sf(data = hamilton_cma,
          fill = "lightgray") +
  geom_sf(data = foodbank_locations,
          aes(size = COVIDClose,
              shape = COVIDClose)) +
  geom_sf(data = inset_box,
          linetype = "dotted",
          color = "red",
          fill = NA) +
  scale_shape_manual(name = "Closed during COVID-19",
                     values = c("Yes" = 4, "No" = 1)) +
  scale_size_manual(values = c("Yes" = 3, "No" = 2)) +
  xlim(-79.975, -79.775) +
  ylim(43.2, 43.3) +
  guides(size = FALSE) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "bottom")

fb / fb_inset
```

```{r plot-low-income-households, echo=FALSE, fig.cap="\\label{fig:low-income-households}Number and proportion of households with incomes less than CAD 40,000."}
lih <- ggplot() +
  geom_sf(data = data_da_2016,
          aes(fill = income_less40k),
          color = NA) +
  geom_sf(data = inset_box,
          linetype = "dotted",
          color = "red",
          fill = NA) +
  scale_fill_viridis_c(name = "Number of households", 
                       option = "A",
                       direction = -1) +
  theme_minimal() +
  theme(axis.text = element_blank(),
        legend.position = "bottom")

p_lih <- ggplot() +
  geom_sf(data = data_da_2016,
          aes(fill = p_inc_less40k),
          color = NA) +
  geom_sf(data = inset_box,
          linetype = "dotted",
          color = "red",
          fill = NA) +
  scale_fill_viridis_c(name = "Proportion of households", 
                       option = "A",
                       direction = -1) +
  theme_minimal() +
  theme(axis.text = element_blank(),
        legend.position = "bottom")

lih / p_lih
```

@@

```{r plot-levels-of-service, echo=FALSE, fig.cap="\\label{fig:levels-of-service}Levels of service at each facility pre-COVID-19 (top panel) and during COVID-19 (bottom panel)."}
## Analysis
# Plot levels of service before and during covid

# Pre-covid
los_pre <- ggplot() +
  geom_sf(data = hamilton_cma) +
  geom_sf(data = los %>%
            filter(timing == "Pre-covid"),
          aes(color = los,
              size = los)) +
  geom_sf(data = foodbank_locations,
          aes(shape = COVIDClose)) +
  scale_color_viridis_c(name = "Level of service pre-COVID-19",
                        option =  "A", 
                        direction = -1) +
  scale_shape_manual(values = c("Yes" = 4, "No" = 1)) +
  guides(size = FALSE, shape = FALSE) +
  theme_minimal() +
  theme(axis.text = element_blank(),
        legend.position = "right")

# During covid
los_covid <- ggplot() +
  geom_sf(data = hamilton_cma) +
  geom_sf(data = los %>%
            filter(timing == "During covid"),
          aes(color = los,
              size = los)) +
  geom_sf(data = foodbank_locations,
          aes(shape = COVIDClose)) +
  scale_color_viridis_c(name = "Level of service during COVID-19",
                        option =  "A", 
                        direction = -1) +
  scale_shape_manual(values = c("Yes" = 4, "No" = 1)) +
  guides(size = FALSE, shape = FALSE) +
  theme_minimal() +
  theme(axis.text = element_blank(),
        legend.position = "right")

los_pre / los_covid
```

```{r plot-levels-of-service-changes, echo=FALSE, fig.cap="\\label{fig:levels-of-service-changes}Changes in levels of service at each facility from pre-COVID-19 to during COVID-19."}
# This figure shows the places where the level of service deteriorated most (excluding the places that closed, where it vanished).
los_change <- los %>%
  st_drop_geometry() %>%
  pivot_wider(names_from = timing, 
              values_from = los, 
              values_fill = 0) %>%
  filter(`During covid` > 0) %>%
  mutate(los_d = `During covid` - `Pre-covid`) %>%
  left_join(foodbank_locations %>%
            transmute(OBJECTID = ID,
                      geometry),
          by = "OBJECTID") %>%
  st_as_sf() %>%
  ggplot() +
  geom_sf(data = hamilton_cma) +
  geom_sf(aes(color = los_d,
              size = los_d)) +
  geom_sf(data = foodbank_locations,
          aes(shape = COVIDClose)) +
  scale_color_viridis_c(name = "Change in level of service",
                        option =  "A", 
                        direction = -1) +
  scale_size(trans = 'reverse') +
  scale_shape_manual(values = c("Yes" = 4, "No" = 1)) +
  guides(size = FALSE, shape = FALSE) +
  theme_minimal() +
  theme(axis.text = element_blank(),
        legend.position = "right")

los_change
```

```{r plot-accessibility, echo=FALSE, fig.align = 'center', out.width = "90%", fig.cap="\\label{fig:accessibility}Accessibility by traffic analysis zone pre-COVID-19 (top panel) and during COVID-19 (bottom panel)."}
## Analysis
# Plot accessibility before and during covid:
acc_pre <- ggplot() +
  #geom_sf(data = hamilton_cma) +
  geom_sf(data = accessibility_taz %>%
            filter(timing == "Pre-covid"),
          aes(fill = accessibility)) +
  scale_fill_viridis_c(name = "Accessibility pre-COVID-19",
                        option =  "A", 
                        direction = -1,
                       breaks = c(0.001,
                                  0.0008,
                                  0.0006,
                                  0.0004,
                                  0.0002),
                       labels = c("0.0010",
                                  "0.0008",
                                  "0.0006",
                                  "0.0004",
                                  "0.0002")) +
  theme_minimal() +
  theme(axis.text = element_blank(),
        legend.position = "right")

acc_covid <- ggplot() +
  #geom_sf(data = hamilton_cma) +
  geom_sf(data = accessibility_taz %>%
            filter(timing == "During covid"),
          aes(fill = accessibility)) +
  scale_fill_viridis_c(name = "Accessibility during COVID-19",
                        option =  "A", 
                        direction = -1,
                       breaks = c(0.0005,
                                  0.0004,
                                  0.0003,
                                  0.0002,
                                  0.0001),
                       labels = c("0.0005",
                                  "0.0004",
                                  "0.0003",
                                  "0.0002",
                                  "0.0001")) +
  theme_minimal() +
  theme(axis.text = element_blank(),
        legend.position = "right")

acc_pre / acc_covid
```

```{r plot-accessibility-changes, echo=FALSE, fig.align = 'center', fig.cap="\\label{fig:accessibility-changes}Changes in accessibility from pre-COVID-19 to during COVID-19."}
## Analysis
# Calculate accessibility change by TAZ:
accessibilty_taz_change <- accessibility_taz %>%
  st_drop_geometry() %>%
  pivot_wider(names_from = timing, 
              values_from = accessibility) %>%
  # Calculate changes in accessibility
  mutate(acc_d = `During covid` - `Pre-covid`) %>%
  # Join TAZ geometry
  left_join(population_age_income %>%
            transmute(TAZUID,
                      geometry),
          by = "TAZUID") %>%
  # Convert to simple features
  st_as_sf()

# Plot
acc_change <- ggplot() +
  #geom_sf(data = hamilton_cma) +
  geom_sf(data = accessibilty_taz_change,
          aes(fill = acc_d),
          color = NA) +
  geom_sf(data = population_age_income,
          fill = NA) +
  scale_fill_viridis_c(name = "Change in accessibility",
                        option =  "A", 
                        direction = 1,
                       breaks = c(-0.0005,
                                  -0.0004,
                                  -0.0003,
                                  -0.0002,
                                  -0.0001),
                       labels = c("-0.0005",
                                  "-0.0004",
                                  "-0.0003",
                                  "-0.0002",
                                  "-0.0001")) +
  theme_minimal() +
  theme(axis.text = element_blank(),
        legend.position = "right")

acc_change
```

@@

### 2021-04-23 Accessibility-Foodbanks-Hamilton/Accessibility-Foodbanks-Hamilton.tex

Data have been prepared for sharing as a data package\footnote{add
  repository}.

@@

Population and income statistics at the level of Dissemination Areas
(DAs) were retrieved using the package \texttt{cancensus} (von Bergmann
et al., 2021). Dissemination Areas are the smallest publicly available
census geography in Canada. We use data from the 2016 Population Census.

@@

We converted all recorded residential parcels in the City of Hamilton to
points on the road network. Each point includes information about the
number of residential units in the parcel. Each residential unit is
``populated'' with the probability of being a ``low income household,''
which we define as having a total household income of less than CAD
40,000. This is approximately the mid-point of the low income cut-off
(LICOs) for families in Canadian cities with populations greater than
500,000 in 2016, to match other Census data (Statistics Canada, 2020b).

\hypertarget{destinations-foodbanks}{%
\subsubsection{Destinations: Foodbanks}\label{destinations-foodbanks}}

The locations of foodbanks were obtained from public records and
geocoded. Three urban sites not in the program were also identified and
geocoded for comparison purposes.

@@

Travel time tables for three modes (car, transit, walking) were computed
using the parcels as the origins and the locations of the foodbanks as
the destinations. For routing, the package \texttt{r5r} (Pereira et al.,
2021b) was used, with a network extract for the City of Hamilton from
OpenStreetMaps and the General Transit Feed Specification from Hamilton
Street Railway, the local transit operator. For routing purposes we used
maximum values of 180 min and 10,000 m walking distance: any destination
that exceeded these thresholds was ignored. The departure time used for
routing was \textbf{TIME}.

@@

Once we obtained travel time tables with population (number of
households) and proportion of trips by mode, we calculated the expected
travel time \(ett\) from each parcel \(i\) to a foodbank \(j\) as
follows: \[
ett_i = p^c_i\cdot tt^c_{ij} + p^t_i\cdot tt^t_{ij} + p^w_i\cdot tt^w_{ij}
\]

\noindent where \(p^k_i\) is the proportion of trips by mode \(k\) in
the TAZ of parcel \(i\), and \(tt^k_{ij}\) is the travel time from
parcel \(i\) to the foodbank. In other words, the expected travel time
is the weighted sum of travel times to the foodbank, with the weights
given by the expected modal split in the TAZ.

@@

\begin{figure}
\includegraphics[width=0.9\linewidth]{Accessibility-Foodbanks-Hamilton_files/figure-latex/plot-results-sensitivity-analysis-1} \caption{\label{fig:sensitivity-analysis}Accessibility as a function of threshold}\label{fig:plot-results-sensitivity-analysis}
\end{figure}

\begin{figure}
\includegraphics[width=0.9\linewidth]{Accessibility-Foodbanks-Hamilton_files/figure-latex/plot-levels-of-service-1} \caption{\label{fig:levels-of-service}Levels of service at each facility pre-COVID-19 (top panel) and during COVID-19 (middle panel). The bottom panel shows the change in level of service.}\label{fig:plot-levels-of-service}
\end{figure}

>>>>

Data have been prepared for sharing as a data package\footnote{add
  repository}. This data package consists of the following:

@@

Population and income statistics for 2016 were retrieved at the level of
Dissemination Areas (DAs) using the package \texttt{cancensus} (von
Bergmann et al., 2021). DAs are the smallest publicly available census
geography in Canada. Income data corresponds to the count of households
by different total income groupings.

@@

We converted all recorded residential land parcels in the City of
Hamilton to points on the road network. Each point includes information
about the number of residential units in the parcel. Next, we define
low-income households as those having a total income of less than
CAD\$40,000, which is approximately the mid-point of the low income
cut-off (LICOs) for families in Canadian cities with populations greater
than 500,000 in 2016, to match other Census data (Statistics Canada,
2020b). We then ``populate'' each residential unit with the probability
of being a low-income household based on the counts of households by
income groups in the DA in which the parcel is located. While this
method assumes a constant probability of low-income household status for
all residential units in a DA, the parcel-level analysis affords a high
level of spatial disaggregation for the accessibility analysis.

\hypertarget{destinations-food-banks-and-food-service-locations}{%
\subsubsection{Destinations: Food Banks and Food Service
Locations}\label{destinations-food-banks-and-food-service-locations}}

The locations of food banks and related food services were obtained from
the Hamilton Public Library's Food Access Guide\footnote{http://foodaccessguide.ca/sites/default/files/partnersites/pdf/foodaccessguide.pdf}.
The guide was updated in April of 2021 to indicate any change affected
on the services due to the pandemic. This includes modified business
hours, a need to make reservations before frequenting, and locations
that have completely shut down in consequence. While some food bank
services have a specific a target population, such as prioritizing
family with young children aged between 0 and 3 or accepting only those
providing proof of low-income status through housing and utility
statements, all the food bank services indicated below are designed to
accommodate those in need of food at zero to low cost. With our focus on
food banks and food services that offer free or low-cost meals at
particular locations, we first removed services such as Meals on Wheels
and other food access services such as food box, community kitchens,
student nutrition programs, and shopping and transportation. In
addition, two free meal services held on different days at the same
location were collapsed into a single service point for the
accessibility analysis.

\caption{\label{tab:table-food-bank-info}\label{tab:food-bank-info}Food Bank and Food Service Information.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{c>{\centering\arraybackslash}p{15em}cc>{\centering\arraybackslash}p{15em}}
\toprule
Type & Description & Locations Pre-COVID & Locations During COVID & Additional Notes\\
\midrule
\cellcolor{gray!6}{Congregate Dining} & \cellcolor{gray!6}{Congregate and dining programs provide low-cost meals that are enjoyed in a community setting. Transportation may be provided} & \cellcolor{gray!6}{7} & \cellcolor{gray!6}{2} & \cellcolor{gray!6}{One remaining location reduced hours during COVID}\\
Community Meals & Programs often run by volunteers that organize suppers, lunches or other get-togethers that give community residents an opportunity to meet one another in a friendly and informal atmosphere while sharing a meal & 11 & 9 & NA\\
\cellcolor{gray!6}{Food Banks} & \cellcolor{gray!6}{Food Banks and Emergency Food programs provide individuals and families with grocery items free of charge} & \cellcolor{gray!6}{27} & \cellcolor{gray!6}{26} & \cellcolor{gray!6}{One remaining location reduced hours during COVID while 4 others moved to appointment only}\\
Free Meals & Meals are provided free of charge in the community through volunteer labour and donations & 9 & 5 & One remaining location reduced hours during COVID\\
\cellcolor{gray!6}{Low-Cost Meals} & \cellcolor{gray!6}{Restaurants, cafeterias and other eating establishments operated by hospitals, senior centers or other organizations which provide reduced-cost meals for low-income people, older adults or other targeted individuals.} & \cellcolor{gray!6}{2} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{The remaining location reduced hours during COVID}\\
\bottomrule
\end{tabular}}
\end{table}

@@

Travel time tables for three modes (car, transit, walking) were computed
using the parcels as the origins and the locations of the foodbanks as
the destinations. For routing, the package \texttt{r5r} (Pereira et al.,
2021b) was used with a network extract for the City of Hamilton from
OpenStreetMaps and the General Transit Feed Specification from Hamilton
Street Railway, the local transit operator. For routing purposes we used
maximum values of 180 min and 10,000 m walking distance: any destination
that exceeded these thresholds was ignored. The departure time used for
routing was \textbf{TIME}.

@@

Once we obtained travel time tables with population (number of
households) and proportion of trips by mode, we calculated the expected
travel time \(ett\) from each parcel \(i\) to a food bank or food
service location \(j\) as follows: \[
ett_i = p^c_i\cdot tt^c_{ij} + p^t_i\cdot tt^t_{ij} + p^w_i\cdot tt^w_{ij}
\]

\noindent where \(p^k_i\) is the proportion of trips by mode \(k\) in
the TAZ of parcel \(i\), and \(tt^k_{ij}\) is the travel time from
parcel \(i\) to the food bank. In other words, the expected travel time
is the weighted sum of travel times to the foodbank, with the weights
given by the expected modal split in the TAZ.

@@

Figure \ref{fig:foodbanks} shows the location of the foodbanks in the
City of Hamilton and their status. Before the pandemic there were 58 of
which 14 closed during the pandemic. As seen in the figure, foodbanks
tend to be predominantly located in the central parts of the city. This
is not surprising: population density is high there, and it is also the
part of the city where lower income households are more numerous in
absolute and relative terms (see Figure
\ref{fig:low-income-households}). Alas, this is also where most of the
closures during the pandemic happened.

\begin{figure}
\includegraphics[width=1\linewidth]{Accessibility-Foodbanks-Hamilton_files/figure-latex/plot-location-foodbanks-1} \caption{\label{fig:foodbanks}Location of foodbanks and operation status; the dotted box is an inset of the central part of the City of Hamilton}\label{fig:plot-location-foodbanks}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{Accessibility-Foodbanks-Hamilton_files/figure-latex/plot-low-income-households-1} \caption{\label{fig:low-income-households}Number and proportion of households with incomes less than CAD 40,000.}\label{fig:plot-low-income-households}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{Accessibility-Foodbanks-Hamilton_files/figure-latex/plot-results-sensitivity-analysis-1} \caption{\label{fig:sensitivity-analysis}Accessibility as a function of threshold}\label{fig:plot-results-sensitivity-analysis}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{Accessibility-Foodbanks-Hamilton_files/figure-latex/plot-levels-of-service-1} \caption{\label{fig:levels-of-service}Levels of service at each facility pre-COVID-19 (top panel) and during COVID-19 (bottom panel).}\label{fig:plot-levels-of-service}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{Accessibility-Foodbanks-Hamilton_files/figure-latex/plot-levels-of-service-changes-1} \caption{\label{fig:levels-of-service-changes}Changes in levels of service at each facility from pre-COVID-19 to during COVID-19.}\label{fig:plot-levels-of-service-changes}
\end{figure}
